Past Lab News

### 2025-03-26 index.qmd
render site

>>>>

<font color="#d08770">[March 03 2025].</font> **New Preprint**. Lalli, M., Al Afif, N., Tang, J., Hasan, H., Dissanayake, E., Sussman, V., Lokesh, R., Rathwell, S., Cashaback, J.G.A., & Carter, M.J. Preferences for costly cooperation are highly individualized. *PsyAr$\chi$iv*. [https://doi.org/10.31234/osf.io/3qaeu_v3](https://doi.org/10.31234/osf.io/3qaeu_v3){target="_blank"}

### 2025-03-26 news.qmd
open application period
render site

---
title: "Lab News"
pagetitle: "CarterLab | News"
toc: false
---

>>>>

---
title: "Past Lab News"
pagetitle: "CarterLab | News"
toc: false
---

<font color="#d08770">[March 03 2025].</font> **New Preprint**. Lalli, M., Al Afif, N., Tang, J., Hasan, H., Dissanayake, E., Sussman, V., Lokesh, R., Rathwell, S., Cashaback, J.G.A., & Carter, M.J. Preferences for costly cooperation are highly individualized. *PsyAr$\chi$iv*. [https://doi.org/10.31234/osf.io/3qaeu_v3](https://doi.org/10.31234/osf.io/3qaeu_v3){target="_blank"}

<font color="#d08770">[January 20 2025].</font> **Announcement**. The application period is now open for students interested in a practicum, project, thesis, or volunteer position in the lab for the 2025-26 academic year. Please see [https://cartermaclab.org/join](https://cartermaclab.org/join) for details.
